Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD

### 2019-10-07 paper/cvpr2020/sections/method.tex
Added SPAD denoising paragraph.

\paragraph{SPAD Denoising}
\begin{itemize}
  \item Talk about histogram matching in the ideal case, jump straight to intensity 
  \item Talk about histogram matching in our case, and how it approaches the
    ideal case. Discuss the following corrections 
    \begin{itemize}
      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
        then the ambient estimate to get rid of the noise floor.
      \item Falloff
    \end{itemize}
  \item Talk about how the histogram matching works with intensity
    considerations applied, briefly.
  \item We don't address jitter or poisson noise.
\end{itemize}
\begin{equation}
  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
\end{equation}
Given a SPAD with histogram $h$ according to the above equation, we first
process the SPAD to remove the effects of some of the terms. First, we

>>>>

\paragraph{SPAD Denoising}
To remove the ambient and dark count photons from the histogram, we apply a
preprocessing step. First, we compute an estimate of the combined ambient
and dark count rate $\hat b$ by averaging $N$ of the first bins together. We then
note that that shining a laser through a 2D diffuser and
measuring a single pixel is very physically similar to recording a single 
non-line-of-sight measurement. We
compute the first difference of the histogram and find the first and last edges 
$i_{first}$ and $i_{last}$ where $\abs{h_i - h_{i+1}}$ is
significantly larger than what would be expected given the rate $b$. From
\cite{Xin2019}, these edges
correspond to the discontinuties in the depth map 
at the closest and furthest image depths, and therefore all of the signal
photons must be in the bins between these two edges. We refine these estimates by
computing $i'_{first} = \max_{i}\mset{i}{h_i > \hat b, i < i_{first}}$ and
$i'_{last} = \min_{i} \mset{i}{h_i > \hat b, i > i_{last}}$
Finally, we reject all photons outside of the valid range by clamping those bins
to 0, and we subtract our ambient estimate from the photons within the valid
range, giving a denoised histogram
\[(h_{denoised})_i = \begin{cases}
    0 & i < i'_{first} \\
    max(h_i - \hat b, 0) & i'_{first} \leq i \leq i'_{last} \\
    0 & i > i'_{last} \\
  \end{cases}.\]
% \begin{itemize}
%   \item Talk about histogram matching in the ideal case, jump straight to intensity 
%   \item Talk about histogram matching in our case, and how it approaches the
%     ideal case. Discuss the following corrections 
%     \begin{itemize}
%       \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
%         then the ambient estimate to get rid of the noise floor.
%       \item Falloff
%     \end{itemize}
%   \item Talk about how the histogram matching works with intensity
%     considerations applied, briefly.
%   \item We don't address jitter or poisson noise.
% \end{itemize}
% \begin{equation}
%   h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
% \end{equation}
% Given a SPAD with histogram $h$ according to the above equation, we first
% process the SPAD to remove the effects of some of the terms. First, we
